### 2020-04-30 final_report/results.tex
change 'used' to 'was trained on'

Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of the
experiments~2-3, we utilised the best-performing hyperparameter
assignments and training sets of varying sizes. In attempts to satisfy
goals~(i) and~(ii) within cross-validation setting, our best surrogate
achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$. These correspond
to the standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{8659251} \times$
with respect to the MC TBR evaluation baseline measured during run~1
(see~\cref{tbl:sampling-runs} for details). While this particular surrogate
used the entire available set of~\num{500000} datapoints, in attempts to satisfy
goal~(iii) we also learned a more simplified model that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
using only a set of size~\num{10000}.

>>>>

Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of the
experiments~2-3, we utilised the best-performing hyperparameter
assignments and training sets of varying sizes. In attempts to satisfy
goals~(i) and~(ii) within cross-validation setting, our best surrogate
achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$. These correspond
to the standard error of regression~$S=\num{0.013}$ and a relative speedup~$\omega=\num{8659251} \times$
with respect to the MC TBR evaluation baseline measured during run~1
(see~\cref{tbl:sampling-runs} for details). While this particular surrogate
was trained on the entire available set of~\num{500000} datapoints, in attempts to satisfy
goal~(iii) we also learned a more simplified model that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
with only a set of size~\num{10000}.
